% K Jonathan Harker's Resume
% Created: 2012-02-11
% Last Modified: 2012-02-11
% Desired Company: Google

% LaTeX resume using res.cls
\documentclass[overlapped]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{20pt} 
\usepackage{geometry}
\geometry{height=8.7in}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf K Jonathan Harker }
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{3338 SW Kelly Ave, Apt 3 \hspace{20pt}  
				Portland, OR 97239 \hspace{20pt}
				(434) 825-7106 \hspace{20pt}
				yuvwah@gmail.com}

\begin{resume}

\section{OBJECTIVE}
\vspace{7pt} % provide vertical space between section title and contents
To contribute to the development of speech recognition software within the open source community.
\section{EDUCATION} 
\vspace{7pt} 
{\sl B.S. Computer Science (minor: Applied Linguistics)} \hfill Portland State University, 2012\\
Major coursework included data structures, discrete mathematics, compiler design, operating system design, machine learning, statistics, and project management. Minor coursework included syntax, phonetics, phonology, conversation analysis, and cognitive science.

{\sl A.S. Computer Science} \hfill Piedmont Virginia Community College, 2008\\
General studies while determining a major.

\section{EXPERIENCE} 
\vspace{7pt} 

{\sl Unix/Linux Systems Administrator, Computer Action Team, Portland State} \hfill 2010-present\\
Develop site configuration using Puppet manifests with custom modules, create site-specific Debian packages, respond to system alerts, and mentor junior devops.

{\sl Student Hacker, Academic \& Research Computing, Portland State} \hfill 2011-present\\
Maintain and optimize a high performance cluster by creating RPM packages of needed software via custom, system-optimized specification files. Troubleshoot network performance issues associated with running on a private VLAN within a larger subnet.

{\sl Computer Science Tutor, Portland State} \hfill 2009-2011\\
Communicate with students to debug C++ code and answer conceptual questions related to object-oriented programming, data structures, and discrete math concepts. Familiarize students with the Linux shell and tools such as SSH, Screen, Git, Vim, and Emacs.

\section{PROJECTS} 
\vspace{7pt} 

{\sl Portland State Autonomous Vehicles Team} \hfill 2011-present\\
Member of a team designing and building an autonomous quadcopter for indoor reconnaissance. Duties include administering embedded Linux, developing device drivers, and writing framing protocols.

{\sl Twitter Relationship Visualization, Tellagence} \hfill 2011-present\\
Member of a six-developer team prototyping a Twitter relationship visualizer for Tellagence, a local startup. Tasks included populating a database and managing the database, and developing an API to facilitate data access for the renderer.

{\sl Audio Filter Pipeline} \hfill 2010-2011\\
Member of a four-person team applying the UNIX pipe concept to audio processing using Go to produce a modular audio processing pipeline. Contributed to the design process, created and coded a delay filter to produce reverb, and developed documentation.

\section{AFFILIATIONS}
\vspace{7pt} 

{\sl Member, Association for Computing Machinery} \hfill 2010-present\\
{\sl Treasurer, Association for Computing Machinery, Portland State University} \hfill 2010-2011\\
{\sl President, Phi Delta Theta Fraternity, Oregon Epsilon} \hfill 2010-2011\\
{\sl Member, Student Organization of Applied Linguistics} \hfill 2009-present\\
{\sl Treasurer, Phi Delta Theta Fraternity, Oregon Epsilon} \hfill 2009-2010\\
{\sl Volunteer Staff, Music and Gaming Festival} \hfill 2006-present

\section{SKILLS} 
\vspace{7pt} 
C/C++, Ruby, Go, LaTeX, Vim, Puppet, Git, shell scripting, Linux, computer clustering, parallel programming, learning algorithms, formant analysis, phonetic/phonological analysis, conversation/discourse Analysis.

\section{HOBBIES} 
\vspace{7pt} 
Rock Climbing, Electric Bass, Live Sound Mixing, Juggling.

\section{LINKS}
\vspace{7pt}
http://www.linkedin.com/profile/view?id=111462980\\
https://github.com/jesusaurus\\
https://github.com/pdxcat\\
http://avt.cecs.pdx.edu\\
http://capstone06.cs.pdx.edu\\
http://code.google.com/p/afp\\

\end{resume}
\end{document}

